Monte Carlo and bootstrap for all parameters with a grid

### 2024-07-27 MC_grid.Rmd
With an example

---
title: "Monte Carlo and bootstrap for all parameteres with a grid"
output: pdf_document
date: "2024-07-26"
---

@@

The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees), variances of these estimators and confidence intervals. The same elements are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations. By comparing the two results, we may verify the invalidity of the bootstrap strategy to find the estimation of the variances.
\\
In this document, one single circle with a radius of 5 is used to compute local variables. Besides, and more importantly, a grid is used for sampling.

@@

# Example:

```

@@

# Example:

```

@@

# Example:

```

@@

# Example:

```

@@

# Example:

```

@@

# Example:

```

@@

# Example:

```

@@

# Example:

```

>>>>

---
title: "Monte Carlo and bootstrap for all parameters with a grid"
output: pdf_document
date: "2024-07-26"
---

@@

The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees), variances of these estimators and confidence intervals. The same elements are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations. By comparing the two results, we may verify the invalidity of the bootstrap strategy to find the estimation of the variances.

In this document, one single circle with a radius of 5 is used to compute local variables. Besides, and more importantly, a grid is used for sampling.

@@

# Example:
## Monte Carlo means of estimations:
##  - for the number of trees: 29529.27
##  - for the volume of trees: 5428.676
##  - for the ratio volume / number of trees: 0.1838376
```

@@

# Example:
## Monte Carlo variances:
##  - for the number of trees: 263478.6
##  - for the volume of trees: 15475.27
##  - for the ratio volume / number of trees: 6.470082e-06
```

@@

# Example:
## 95% confidence intervals using the normal method:
##  - for the number of trees: [ 28787.75 ; 30799.86 ]
##  - for the volume of trees: [ 5115.539 ; 5603.177 ]
##  - for the ratio volume / number of trees: [ 0.1748962 ; 0.1848671 ]
```

@@

# Example:
## 95% confidence intervals using the percentile method:
##  - for the number of trees: [ 28533.3 ; 30557.75 ]
##  - for the volume of trees: [ 5188.069 ; 5673.772 ]
##  - for the ratio volume / number of trees: [ 0.1787598 ; 0.1888164 ]
```

@@

# Example:
## 95% confidence intervals using the reverse percentile method:
##  - for the number of trees: [ 29029.86 ; 31054.31 ]
##  - for the volume of trees: [ 5044.944 ; 5530.647 ]
##  - for the ratio volume / number of trees: [ 0.1709469 ; 0.1810035 ]
```

@@

# Example:
## Mean of the means of estimations obtained through each bootstrap process:
##  - for the number of trees: 29546.03
##  - for the volume of trees: 5431.112
##  - for the ratio volume / number of trees: 0.1838134
```

@@

# Example:
## Mean of the variance of bootstrap samples:
##  - for the number of trees: 2630037
##  - for the volume of trees: 99634.96
##  - for the ratio volume / number of trees: 1.033748e-05
```

@@

# Example:
## Difference between the two estimations of variance:
##  - for the number of trees: 898.1975%
##  - for the volume of trees: 543.8335%
##  - for the ratio volume / number of trees: 59.77348%
```
